\def\year{2016}
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algpseudocode} %format of the algorithm
\usepackage{color}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{amsmath, bm}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{ulem}
\normalem
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{PKUICST at TREC 2016 Real-Time Summarization Track:\\
Push Notifications and Email Digest
}
\author{Lili Yao \quad Chao Lv \quad Feifan Fan \quad Jianwu Yang\footnote{Corresponding author} \quad Dongyan Zhao\\
\{yaolili, lvchao, fanff, yangjw, zhaody\}@pku.edu.cn\\
\\
Institute of Computer Science and Technology\\
Peking University, Beijing 100871, China\\
}

\maketitle
\begin{abstract}
\begin{quote}
This paper describes our approaches for the TREC 2016 Real-Time Summarization track,
including push notifications scenario and email digest scenario.
In the push notifications scenario, we mainly focus on designing a real-time system,
which listens to the Twitter sample stream and makes the push actions for the given topics.
Low coupling modules are utilized to obtain the timely, relevant and novel features.
In the email digest scenario, we apply the language model combined
with the external knowledge base, i.e. Google, for query expansion.
Besides, different text similarity algorithms are tried, such as nagetive KL-divergence and Simhash.
Experimental results show that our two-stage filtering methods achieve good performance
with respect to EG1 and nCG1 metrics for push notifications scenario.
In addition, our systems for email digest scenario also obtain convincing nDCG1 scores.
\end{quote}
\end{abstract}

\input{sec-intro}
\input{sec-method}
\input{sec-a}
\input{sec-b}
\input{sec-exp}
\input{sec-con}

\section{Acknowledgments}
The work reported in this paper is supported by the National Natural Science Foundation of China Grant 61370116.

\bibliographystyle{aaai}
\bibliography{yelp}
\end{document}
